NIRCam Faint and Bright Flux Calibration Plan

### 2017-05-08 ms.tex
I added a few more details about the reference sphere observations with MSX.

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the MSX calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Space Experiment (MSX) calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).

@@

The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require unfeasibly long integration times so the bright calibrators are preferred for steps 2 and 3.

>>>>

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black.
Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event.

@@

Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with MSX calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require unfeasibly long integration times so the bright calibrators are preferred for steps 2 and 3.
